---
title: "Oscillation Indices"
author: "Fernando A. Campos"
date: "`r Sys.Date()`"
output:
  md_document:
    variant: markdown_github
vignette: >
  %\VignetteIndexEntry{Oscillation Indices}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

[Back to Respository](https://github.com/camposfa/ClimGrid)

```{r, message = FALSE, warning = FALSE, echo = FALSE} 
  Sys.setenv(TZ = 'UTC')

  library(ClimGrid)
```

## Utility functions for climate data

`ClimGrid` includes functions for pulling the most recent data for several large-scale climate oscillation indices from various online data repositories. Supported climate indices include:

- Niño 1+2 Monthly ERSSTv4 ("nino1.2")
- Niño 3 Monthly ERSSTv4 (""nino3")
- Niño 4 Monthly ERSSTv4 ("nino4")
- Niño 3.4 Monthly ERSSTv4 ("nino3.4")
- Southern Oscillation Index ("soi")
- Oceanic Niño Index ("oni"), same as 3-month running average in Niño 3.4
- Multivariate ENSO Index ("mei")
- Dipole Mode index ("dmi")
- Pacific Decadal Oscillation ("pdo")
- Atlantic Multidecadal Oscillation ("amo")
- North Atlantic Oscillation ("nao")
- Southern Annular Mode ("sam")

The function `load_climate_index` returns a named list of monthly climate index data. Each element of the list is an object of class `dplyr::tbl_df`.

```{r}
  indices <- load_climate_index(c("nao", "mei"))
  
  indices
```

Squash all the list elements together to a single `tbl_df` with `dplyr::bind_rows`:

```{r}
  indices_df <- dplyr::bind_rows(indices)
  summary(indices_df)
```
