---
title: "ClimGrid Vignette"
author: "Fernando A. Campos"
date: "`r Sys.Date()`"
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ClimGrid

`ClimGrid` is a collection of functions for obtaining and analyzing gridded climate data and global climate oscillation indices.

Additional functionality and documentation will be added soon.


## Preparation

To use this package, you first need to install `devtools` with:
```{r, eval = FALSE}
    install.packages("devtools")
```

Then, you can install the latest development version of `ClimGrid` from github:

```{r, eval = FALSE}
  library(devtools)
  devtools::install_github("camposfa/ClimGrid")
```

After you have installed the package once, you can simply load it in the future using:

```{r, message = FALSE, warning = FALSE} 
  library(ClimGrid)
```

This package makes heavy use of the data manipulation packages [stringr](http://cran.r-project.org/package=stringr), [lubridate](http://cran.r-project.org/package=lubridate), [tidyr](http://cran.r-project.org/package=tidyr), and [dplyr](http://cran.r-project.org/package=dplyr). If not already installed, `ClimGrid` will install these packages automatically.

## Vignettes

[Obtaining and analyzing climate oscillation index data](Climate.md)
